Data Analysis Expanded

### 2019-08-25 data_analysis/data_analysis_expanded.Rmd
bug fix

```{r s1_m4_c}
set.seed(2423)
s1_m4_c <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(50,150,by=5),
                              multiplier = 200,
                              c_seq_len = 200,
                              starts = data.frame(alpha = 0.005779,
                                                  delta = 0.002530))
```
```{r s1_m4_c_print, results = 'asis'}
s1_m4_c %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```

@@

For each method and sample we save the most refined or best estimate.
```{r output_data}
sample_1 <- list(method_0 = s1_m0_b$best,
                 method_1 = s1_m1_d$best,
                 method_2 = s1_m2_c$best,
                 method_3 = s1_m3_c$best,
                 method_4 = s1_m4_c$best)

sample_2 <- list(method_0 = s2_m0_b$best,
                 method_1 = s2_m1_c$best,
                 method_2 = s2_m2_c$best,
                 method_3 = s2_m3_d$best,
                 method_4 = s2_m4_c$best)

sample_3 <- list(method_0 = s3_m0_b$best,
                 method_1 = s3_m1_d$best,
                 method_2 = s3_m2_c$best,
                 method_3 = s3_m3_d$best,
                 method_4 = s3_m4_c$best)

>>>>

```{r s1_m4_c}
#set.seed(2423)
#s1_m4_c <- rre::cv_replicates(list_of_samples[[2]],
#                              eval_function = "gof_chi_sq",
#                              partitions = 5,
#                              lambda_vec = seq(50,150,by=5),
#                              multiplier = 200,
#                              c_seq_len = 200,
#                              starts = data.frame(alpha = 0.005779,
#                                                  delta = 0.002530))
```
```{r s1_m4_c_print, results = 'asis'}
#s1_m4_c %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```

@@

For each method and sample we save the most refined or best estimate.
```{r output_data}
sample_1 <- list(method_0 = s1_m0_b$best,
                 method_1 = s1_m1_d$best,
                 method_2 = s1_m2_c$best,
                 method_3 = s1_m3_d$best,
                 method_4 = s1_m4_b$best)

sample_2 <- list(method_0 = s2_m0_b$best,
                 method_1 = s2_m1_c$best,
                 method_2 = s2_m2_c$best,
                 method_3 = s2_m3_e$best,
                 method_4 = s2_m4_c$best)

sample_3 <- list(method_0 = s3_m0_b$best,
                 method_1 = s3_m1_d$best,
                 method_2 = s3_m2_c$best,
                 method_3 = s3_m3_e$best,
                 method_4 = s3_m4_c$best)
